\textbf{Towards File System integrity verification in BTRFS}

### 2019-07-30 paper.tex
Add bibliography entries for UBIFS.

\subsection{UBIFS}
UBIFS is the Linux Kernel's File System typically used in the Embedded Device
Market, where raw flash chips are used as opposed to traditional Hard Disk
Drives or Solid State Disks.\\
UBIFS also has the capability of authenticating the File System. Similar to
what is proposed for BTRFS in this paper, UBIFS is using a HMAC to protect
it's internal on-disk data structures as well as the file data stored on the
File System.

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\bibitem{FS-VERITY}
	J. Corbet
	\textit{Protecting files with fs-verity}
	\\\texttt{\href{https://lwn.net/Articles/763729/}{https://lwn.net/Articles/763729/}}
\end{thebibliography}
\end{document}

>>>>

\subsection{UBIFS}
UBIFS\cite{UBIFS} is the Linux Kernel's File System typically used in the
Embedded Device Market, where raw flash chips are used as opposed to
traditional Hard Disk Drives or Solid State Disks.\\ UBIFS also has the
capability of authenticating the File System. Similar to what is proposed for
BTRFS in this paper, UBIFS is using a HMAC to protect it's internal on-disk
data structures as well as the file data stored on the File System.

@@

\begin{thebibliography}{9}
\bibitem{BTRFS}
	Ohad Rodeh, Josef Bacik and Chris Mason.
	\textit{BTRFS: The Linux B-tree Filesystem}
	\\\texttt{https://domino.research.ibm.com/library/cyberdig.nsf\\/papers/6E1C5B6A1B6EDD9885257A38006B6130/\$File/rj10501.pdf}
	\\IBM Research, Fusion-IO.
\bibitem{rodeh}
	Ohad Rodeh.
	\textit{B-trees, shadowing, and clones}
	\\\texttt{\href{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}{https://www.usenix.org/legacy/events/lsf07/tech/rodeh.pdf}}
	USENIX Linux Storage \& Filesystem Workshop 2007. Also Rodeh, Ohad (2008). "B-trees, shadowing, and clones". ACM Transactions on Storage.
\bibitem{maid}
	Wikipedia.
	\textit{Evil Maid Attack}
	\\\texttt{\href{https://en.wikipedia.org/wiki/Evil\_maid\_attack}{https://en.wikipedia.org/wiki/Evil\_maid\_attack}}
\bibitem{IMA}
	Linux IMA Project
	\textit{IMA - Integrity Measurement Atchitecture}
	\\\texttt{\href{http://linux-ima.sourceforge.net/}{http://linux-ima.sourceforge.net/}}
\bibitem{HMAC}
	H. Krawczyk, M. Bellare, R. Canetti
	\textit{HMAC: Keyed-Hashing for Message Authentication}
	\\\texttt{\href{https://tools.ietf.org/html/rfc2104}{https://tools.ietf.org/html/rfc2104}}
	Request for Comments: 2104 	
\bibitem{FS-VERITY}
	J. Corbet
	\textit{Protecting files with fs-verity}
	\\\texttt{\href{https://lwn.net/Articles/763729/}{https://lwn.net/Articles/763729/}}
\bibitem{UBIFS}
	S. Hauer.
	\textit{UBIFS Authentication}
	\\\texttt{\href{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}{https://www.kernel.org/doc/Documentation/filesystems/ubifs-authentication.md}}
\end{thebibliography}
\end{document}
